SPP-Perc: Peceptron Learning Based Enhanced Signature Path Prefetcher

### 2018-11-15 paper_1.tex
Version 2.3
Consolidated the bibliography

\section{Introduction}
Since past few decades, processor and memory scaling has been enabled with different philosophies in mind. 
While processor scaling focused on speed improvements, memory scaling was centred around increasing the storage capacity. 
The process technology reaching scaling limitations led to Memory Wall [cite] - the increasing performance gap between the processor speed and the memory speeds. 
Various techniques have been developed to combat this widening gap. 
Data prefetching is one such important technique. 
Data prefetching exploits the fact that in most applications, memory accesses have a well-defined pattern.

@@

\begin{itemize}
\item This is the first time where a truly on-line learning based neural network model has been used when it comes to hardware data prefetching. 
The prior works in this area either relied on program semantics [cite] or were application specific [cite] or could not yield a significant improvement over the baseline prefetcher used. [cite]

@@

\subsection{Related Work}
Some of the earliest data prefetchers developed to leverage this locality were stride based [cite:\newline
- A. J. Smith. Sequential Program Prefetching in Memory Hierarchies (1978)\newline
- J.-L. Baer and T.-F. Chen. An Effective On-Chip Preloading Scheme to Reduce Data Access Penalty (1991)\newline
]\newline

Major research in prefetching domain was based on stride length and depth prediction [cite:\newline
- Decoupled Predictor-Directed Stream Prefetching
Architecture (2003)\newline
- Memory Prefetching Using Adaptive Stream Detection (2006)\newline
]\newline

With time newer and more intricate prefetchers were introduced. [Cite:\newline
- Temporal Streaming of Shared Memory (2005)\newline
- Stealth Prefetching (2006)\newline
- Feedback Directed Prefetching: Improving the Performance and Bandwidth-Efficiency of Hardware Prefetchers (2007)\newline
- Coordinated Control of Multiple Prefetchers in Multi-Core Systems (2009)\newline
- Techniques for Bandwidth-Efficient Prefetching of Linked Data Structures in Hybrid Prefetching Systems (2009)\newline
- PACMan: PrefetchAware Cache Management for High Performance Caching (2011)\newline
- TLB Improvements for Chip Multiprocessors: Inter-Core Cooperative Prefetchers and Shared Last-Level TLBs (2013)\newline
- Linearizing Irregular Memory Accesses for Improved Correlated Prefetching (2013)\newline
- Sandbox Prefetching: Safe run-time evaluation of aggressive prefetchers\newline
]\newline

Prefetchers often tend to correlate predictions with the past memory access addresses [cite: Making Address-Correlated Prefetching Practical (2010)]. 
 A whole class of streaming prefetchers developed on the lines of Spatial / Temporal Memory Streaming
[ Cite:\newline
- Accurate and Complexity-Effective Spatial Pattern Prediction (2004)\newline
- Spatial Memory Streaming (2006)\newline
- Temporal Instruction Fetch Streaming (2008)\newline
- Practical Off-Chip Meta-Data for Temporal Memory Streaming (2009)\newline
- Spatio-Temporal Memory Streaming (2009)\newline
- Spatial Memory Streaming with Rotated Patterns (2009)\newline
- Spatial Memory Streaming.” Journal of Instruction-Level Parallelism" (2011)\newline
]\newline

More modern prefetchers are often offset based <cite BOP and other offset based> or lookahead based <cite SPP, KPC and a few more>.

A related line of work also explored cache replacement: insertion policies and dead block prediction, with an eye towards prefetching. [Cite:\newline
- Dead-Block Prediction and Dead-Block Correlating Prefetchers (2001)\newline
- Cache Bursts: A New Approach for Eliminating Dead Blocks and Increasing Cache Efficiency (2008)\newline
- KPC (2017)\newline
- Rethinking Belady's Algorithm to Accommodate Prefetching (2018)\newline
]

There have been attempts at introducing Machine Learning based elements into prefetching. 
The paper Semantic Locality and Context-based Prefetching Using Reinforcement Learning[cite] by Peled \textit{et.al.} introduces interesting ideas for on-line Reinforcement Learning and dynamically scaling the magnitude of feedback given to the baseline prefetcher. 
The biggest challenge here is that it relies on compiler support for getting features to build the context.

Another notable research in the domain was done by Liao \textit{et. al.} [cite Machine Learning-Based Prefetch Optimization for Data Center Applications].
Their work focuses specifically on prefetching for data center applications. 
They use offline Machine Learning Algorithms like Support Vector Machines, Logistic Regressions, and Tree-based Classification for parametric search for coming up with an optimal prefetcher configuration.

\textit{<Note: The below paper is literally the same idea as ours. But poor implementation and no good results. How much to bash this paper?>}
Finally, the paper on Data Cache Prefetching with Perceptron Learning[cite] talks about the idea of two step prefetching.
The first step is an existing prefetcher like Stride Prefetcher or a Markov Prefetcher while the second step is a perceptron based throttler.
The paper has lots of limitations in terms of design and implementation.
That reflects in the fact that it did not lead to any significant performance gain over even the basic prefetchers like the Stride Prefetcher[cite] and the Markov Prefetcher[cite]

@@

Perceptron learning for computer architecture design has been around for a while. 
It was popularized by [cite initial branch prediction paper]. 
In it's original implementation, the Program Counter of the instruction looking for a branch prediction would index into a given table of perceptron weights. 
The retrieved weights would then be multiplied with the history of branch outcomes stored in the History Register (which is a feature) in a dot product fashion. 
The sum obtained is thresholded at 0 \textit{i.e.}, if the prediction y\textsubscript{out} >= 0, the prediction is made as \textit{true}, or branch taken.
Else if the sum is < 0, the prediction is made as \textit{false}.

The structure that we use is derived from the model introduced in [cite piecewise linear branch prediction]. 
Here the feature itself is used to index into a hash of perceptron weights. 
This form of indexing makes sure that the hyper-plane learned by the perceptron weights is able to differentiate between linearly inseparable outcomes. 
\textit{<Is it true? Not sure>}

Perceptron Learning for Reuse Prediction [cite] extended the hash perceptron architecture to perform prediction in context of cache replacement. 
Perceptron layer can learn to correlate the cache replacement behaviour with a variety of features. 
Each feature has its dedicated table of perceptron weights which it indexes into. 
Hence number of tables equals the number of features. 
Once the perceptron weights from all the tables are obtained, they're summed and thresholded based on a pre-decided value. 
This led to a prediction mechanism that is highly accurate, has quick learning rate and is adaptable to changing program behaviour. 
The features introduced in that paper were derived from Program Counters of the current and the last few instructions and the memory address of the current access. 
Even with such basic features, high level of correlation could be established by perceptrons.

The work was further extended by Multiperspective Reuse Prediction[cite], which introduced a varied set of parametric features. 
Although design space exploration for feature and parameter selection was a non-trivial task, once fixed, it could give a cache replacement predictor highly suitable for the given set of applications.
\newline
\newline
\textit{Deviations From Actual Perceptrons:} Traditionally, a perceptron prediction involves multiplying the vector of input features: F\textsubscript{1xN}, with the corresponding weight vector: W\textsubscript{Nx1} in a dot product fashion to obtain the sum y\textsubscript{out}. 
Here what we use is a perceptron-like structure. 
The feature is used to hash into the weight of perceptrons and the retrieved weights are added straight away. 
This can be seen a dot product of $\vec{1}$\textsubscript{1xN} with W\textsubscript{Nx1}. 
This way, the perceptron algorithm doesn't introduce any multiplication operations in the inference or training process. 
Hence what we adapt in this work, is a perceptron-like learning algorithm as it involves the same principle involved in perceptron inferencing and training. 
For simplicity, we will call our implementation as perceptron implementation.
\newline
\newline
\textit{Perceptron Update Rule:} In all the above implementations, a uniform perceptron update principle is being followed. 
The weights need to be updated if the prediction was wrong or the predicted sum does not cross a certain threshold. 
After a certain training period, these weights are proportional to the probability of the outcome being true. 
This training threshold makes sure that the perceptrons are trained till a certain level of confidence and yet they are not over-trained to the given set. 
Care is taken that the weights saturate at certain positive and negative values so that they remain confined to the bit-width. 
The same rules will be applied in the discussion done in section XX on SPP-Perc learning algorithm.

\subsection{Signature Path Prefetcher Architecture}
Since the work we have done builds heavily on SPP[cite], we are presenting a brief recap of the ideas introduced in the original paper, especially with an eye towards their relevance in our work. 
Signature Path Prefetcher (SPP) is a lookahead prefetcher and consists of following structural components:
\newline
\newline
\textbf{Signature Table:} ST keeps track of 256 most recently accessed pages. 
It is meant to capture memory access patterns within a page boundary. 
SPP indexes into an entry of ST using the page number. 
For each entry corresponding to a page, ST stores the `last block offset' and `old signature'. 
Last block offset is the block offset of the last memory access of that given page. 
The block offset is calculated with respect to the page boundary. 
The signature is a 12-bit compressed representation of the past few memory accesses for that page. 
The signature is calculated as:
$$New Signature = (\,Old Signature << 3 bits\,) \;\;XOR\;\; (\,Delta\,)$$ 
In case a matching page entry is found, the stored signature in the corresponding entry is retrieved.
\newline
\newline
Consider the case that incoming page number 10 with a block offset 3 finds a match in the ST. 
The retrieved pattern signature is 0x30 and the Last Offset is 1. 
Since now there is the Last Block Offset (1), Incoming Block Offset (3), Old Signature (0x30), and New Signature calculated as per above equation (0x182), SPP can infer non-speculatively that the given pattern of memory accesses (as captured in the Old Signature) leads to the particular Delta. 
In general, Delta is defined as the difference between the prefetch suggestion block and the initial block which triggered the prefetch. 
In this case, since SPP is in learning phase, it is defined as the difference between the Incoming Block Offset and the Last Block Offset (+2 in this case). 
This, in turn generates the new memory pattern (New Signature). 
This newly learned signature pattern and the delta is stored in the Pattern Table.
\newline
\newline
\textbf{Pattern Table:} The PT is indexed by the signature generated from ST. 
PT holds predicted delta patterns and their confidence estimates. 
Each entry indexed by the signature holds up to 4 unique delta predictions. 
This is implemented by making PT as a 4-way associative table. 
To measure an estimate of a delta confidence, PT implements two counters: C\textsubscript{sig} for each entry indexed by the signature and C\textsubscript{delta} for each delta entry for a given signature. 
More details of this on-line score-keeping mechanism is described under Confidence Tracking discussion.

@@

\item \textbf{Program Counter XOR Depth}: PC is for the instruction which triggered the prefetch chain.
Depth refers to the iteration count of the lookahead stages.
In general, PC is not considered as a good basis for doing lookahead prefetching as all the prefetches with depth >= 1 gets aliased onto the same PC which won't be true in actual demand fetch case.
This feature resolves a PC into a different value for each lookahead depth of SPP speculation, giving a more accurate correlation in lookahead cases.
This is akin to the concept of Virtual Program Counters [cite] introduced by Kim \textit{et. al.} for indirect branch prediction.

@@

\section{METHODOLOGY}
\subsection{Performance Model}
For testing and comparing SPP-Perc, we used ChampSim [cite] simulator. 
ChampSim is an enhanced version of the framework that was used for the 2nd Data Prefetch Championship (DPC-2)[cite]. 
We model model a 1-core / 4-core / 8-core Out of Order machine. The details of the configuration parameters is summarized in Table  \ref{tab:Sim_params}.

@@

The block size was fixed 64KB. Prefetching was only triggered at L2 Cache demand accesses but could be sent to L2 Cache or Last Level Cache. 
No L1 Data level prefetching was done. 
LRU replacement policy was used on all levels of cache hierarchies. 
Branch prediction was done using the perceptron branch predictor [cite]. 
Page size was kept as 4KB. 
Champsim operates all the prefetchers strictly in the physical address space.

@@

\subsection{Workloads}
This is the first time that SPEC 2017 benchmark suite[cite] has been used to characterize and measure the prefetch performance. 
We use all the 20 workloads available in the SPEC 2017 Suite. 
Using SimPoint[cite] methodology, we identified 95 different program segments of 1 Billion instructions each.

We performed cross-validation of our SPP-Perc model using SPEC 2006 and CloudSuite benchmarks.
For SPEC 2006, we developed 94 simpoints spread across the 29 applications.
For CloudSuite, we used the traces made available for the 2nd Cache Replacement Competition (CRC-2) [cite].
The traces include 4 multi-core applications with 6 distinct phases per application. 
In total, we used 285 traces representing workloads across 53 applications.

@@

\subsection{Preferchers Simulated}
We compared SPP-Perc against three of the latest state of the art prefetchers: Best Offset Prefetcher (BOP)[cite], DRAM Aware - Access Map Pattern Matching (DA-AMPM) [cite] and Signature Path Prefecher (SPP)[cite]. 
BOP was the winner in 2nd Data Prefetching Championship[cite]. 
DA-AMPM is the enhanced version of AMPM[cite], modified to account for DRAM row buffer locality. 
SPP has been shown to outperform BOP on SPEC 2006 traces[cite]. 
For each of these, we compare their speedups taking no prefetching as the baseline.

@@

%%%%%%%%% -- BIB STYLE AND FILE -- %%%%%%%%
%%\bibliographystyle{ieeetr}
%%\bibliography{ref}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\section{Introduction}
Since past few decades, processor and memory scaling has been enabled with different philosophies in mind. 
While processor scaling focused on speed improvements, memory scaling was centred around increasing the storage capacity. 
The process technology reaching scaling limitations led to Memory Wall\cite{MemWall} - the increasing performance gap between the processor speed and the memory speeds. 
Various techniques have been developed to combat this widening gap. 
Data prefetching is one such important technique. 
Data prefetching exploits the fact that in most applications, memory accesses have a well-defined pattern.

@@

\begin{itemize}
\item This is the first time where a truly on-line learning based neural network model has been used when it comes to hardware data prefetching. 
The prior works in this area either relied on program semantics\cite{Semantics} or were application specific\cite{Datacenter} or could not yield a significant improvement over the baseline prefetcher used\cite{BadPerc}.

@@

\subsection{Related Work}

The idea of prefetching has been around since Instruction Stream Buffers were proposed by Jouppi.
\cite{ISB}
Some of the earliest data prefetchers developed to try to identify memory access patterns with a constant stride pattern.
\cite{Smith} 
\cite{Baer}
\cite{Stride}
Major research was dedicated to stride distance and depth prediction.
\cite{Decoupled}
\cite{Adaptive}
Newer prefetchers aimed at correlating predictions with the past memory access addresses.
\cite{Address_Correlated} 
\cite{AMPM}

With time newer and more intricate prefetchers were introduced.
\cite{Wenisch_Temporal_Streaming}
\cite{Stealth}
\cite{Feedback_Directed}
\cite{Coordinated}
\cite{Bandwidth_Efficient}
\cite{Pacman}
\cite{TLB}
\cite{Linearizing}
\cite{Sandbox}
\cite{VLDP}
\cite{DoL}
\cite{Domino}
A whole class of streaming prefetchers developed on the lines of Spatial / Temporal Memory Streaming.
\cite{Spatial_Pattern}
\cite{SMS}
\cite{Temporal_Instruction_Fetch}
\cite{Off_Chip}
\cite{STMS}
\cite{SMS_JILP}

Most modern prefetchers aim at identifying complex memory access patterns in a given application. 
This allows them to capture some of the irregular patterns seen in pointer chasing data-structures.
Offset based prefetchers are a generalization of the next-line prefetcher.
Some of the prominent prefetchers exploiting this idea are
Sandbox Prefetcher \cite{Sandbox}
and the Best Offset Prefetcher \cite{BOP}
Another class of prefetchers is lookahead Prefetchers.
Such prefetchers try to speculate deep into the application's memory access trail.
These include Path Confidence based Lookahead Prefetching \cite{SPP}
and Kill the Program Counter \cite{KPC}.

A related line of work also explores cache replacement - insertion policies and dead block prediction, with an eye towards prefetching. 
\cite{DB_Pred}
\cite{Cache_Burst}
\cite{KPC}
\cite{Harmony}
Nori \textit{et.al.} introduced prefetching with  respect to runtime criticality.
\cite{CATCH}
\newline

\textit{Machine Learning and Prefetching:}
Peled \textit{et.al.} introduce interesting ideas for on-line Reinforcement Learning and dynamically scaling the magnitude of feedback given to the baseline prefetcher.
\cite{Semantics}
The biggest challenge here is that it relies on compiler support for getting features to build the context.

The paper by Liao \textit{et. al.} focuses on prefetching for data center applications.
\cite{Datacenter}
They use offline Machine Learning Algorithms like SVMs and Logistic Regressions to do parametric search for an optimal prefetcher configuration.

%% NOTE: The below paper is literally the same idea as ours. But poor implementation and no good results. How much to bash this paper?
Finally, the paper on Data Cache Prefetching with Perceptron Learning\cite{BadPerc} talks about the idea of two step prefetching.
The first step is an existing baseline prefetcher while the second step is a perceptron based throttler.
The paper has lots of limitations in terms of design and implementation.
That reflects in the fact that it did not lead to any significant performance gain over even the basic prefetchers like the Stride Prefetcher\cite{Stride} and the Markov Prefetcher\cite{Markov}.

et. al.

@@

Perceptron learning for computer architecture design has been around for a while. 
It was first popularized by Jimenez \textit{et. al.} in for doing branch prediction. \cite{Perc_Branch} 
In it's original implementation, the Program Counter of the instruction looking for a branch prediction would index into a given table of perceptron weights. 
The retrieved weights would then be multiplied with the history of branch outcomes stored in the History Register (which is a feature) in a dot product fashion. 
The sum obtained is thresholded at 0 \textit{i.e.}, if the prediction y\textsubscript{out} >= 0, the prediction is made as \textit{true}, or branch taken.
Else if the sum is < 0, the prediction is made as \textit{false}.

The structure that we use is derived from the model introduced in Piecewise Linear Branch Prediction\cite{Piece_Linear}. 
Here the feature itself is used to index into a hash of perceptron weights. 
This form of indexing makes sure that the hyper-plane learned by the perceptron weights is able to differentiate between linearly inseparable outcomes. 
\textit{<Is it true? Not sure>}

Perceptron Learning for Reuse Prediction\cite{Perc_Reuse} extended the hash perceptron architecture to perform prediction in context of cache replacement. 
Perceptron layer can learn to correlate the cache replacement behaviour with a variety of features. 
Each feature has its dedicated table of perceptron weights which it indexes into. 
Hence number of tables equals the number of features. 
Once the perceptron weights from all the tables are obtained, they're summed and thresholded based on a pre-decided value. 
This led to a prediction mechanism that is highly accurate, has quick learning rate and is adaptable to changing program behaviour. 
The features introduced in that paper were derived from Program Counters of the current and the last few instructions and the memory address of the current access. 
Even with such basic features, high level of correlation could be established by perceptrons.

The work was further extended by Multiperspective Reuse Prediction\cite{Multiperspective}, which introduced a varied set of parametric features. 
Although design space exploration for feature and parameter selection was a non-trivial task, once fixed, it could give a cache replacement predictor highly suitable for the given set of applications.
\newline
\newline
\textit{Deviations From Actual Perceptrons:} Traditionally, a perceptron prediction involves multiplying the vector of input features: F\textsubscript{1xN}, with the corresponding weight vector: W\textsubscript{Nx1} in a dot product fashion to obtain the sum y\textsubscript{out}. 
Here what we use is a perceptron-like structure. 
The feature is used to hash into the weight of perceptrons and the retrieved weights are added straight away. 
This can be seen a dot product of $\vec{1}$\textsubscript{1xN} with W\textsubscript{Nx1}. 
This way, the perceptron algorithm doesn't introduce any multiplication operations in the inference or training process. 
Hence what we adapt in this work, is a perceptron-like learning algorithm as it involves the same principle involved in perceptron inferencing and training. 
For simplicity, we will call our implementation as perceptron implementation.
\newline
\newline
\textit{Perceptron Update Rule:} In all the above implementations, a uniform perceptron update principle is being followed. 
The weights need to be updated if the prediction was wrong or the predicted sum does not cross a certain threshold. 
After a certain training period, these weights are proportional to the probability of the outcome being true. 
This training threshold makes sure that the perceptrons are trained till a certain level of confidence and yet they are not over-trained to the given set. 
Care is taken that the weights saturate at certain positive and negative values so that they remain confined to the bit-width. 
The same rules will be applied in the discussion done in section XX on SPP-Perc learning algorithm.

\subsection{Signature Path Prefetcher Architecture}
Since the work we have done builds heavily on SPP\cite{SPP}, we are presenting a brief recap of the ideas introduced in the original paper, especially with an eye towards their relevance in our work. 
Signature Path Prefetcher (SPP) is a lookahead prefetcher and consists of following structural components:
\newline
\newline
\textbf{Signature Table:} ST keeps track of 256 most recently accessed pages. 
It is meant to capture memory access patterns within a page boundary. 
SPP indexes into an entry of ST using the page number. 
For each entry corresponding to a page, ST stores the `last block offset' and `old signature'. 
Last block offset is the block offset of the last memory access of that given page. 
The block offset is calculated with respect to the page boundary. 
The signature is a 12-bit compressed representation of the past few memory accesses for that page. 
The signature is calculated as:
$$New Signature = (\,Old Signature << 3 bits\,) \;\;XOR\;\; (\,Delta\,)$$ 
In case a matching page entry is found, the stored signature in the corresponding entry is retrieved.
\newline
\newline
Consider the case that incoming page number 10 with a block offset 3 finds a match in the ST. 
The retrieved pattern signature is 0x30 and the Last Offset is 1. 
Since now there is the Last Block Offset (1), Incoming Block Offset (3), Old Signature (0x30), and New Signature calculated as per above equation (0x182), SPP can infer non-speculatively that the given pattern of memory accesses (as captured in the Old Signature) leads to the particular Delta. 
In general, Delta is defined as the difference between the prefetch suggestion block and the initial block which triggered the prefetch. 
In this case, since SPP is in learning phase, it is defined as the difference between the Incoming Block Offset and the Last Block Offset (+2 in this case). 
This, in turn generates the new memory pattern (New Signature). 
This newly learned signature pattern and the delta is stored in the Pattern Table.
\newline
\newline
\textbf{Pattern Table:} The PT is indexed by the signature generated from ST. 
PT holds predicted delta patterns and their confidence estimates. 
Each entry indexed by the signature holds up to 4 unique delta predictions. 
This is implemented by making PT as a 4-way associative table. 
To measure an estimate of a delta confidence, PT implements two counters: C\textsubscript{sig} for each entry indexed by the signature and C\textsubscript{delta} for each delta entry for a given signature. 
More details of this on-line score-keeping mechanism is described under Confidence Tracking discussion.

@@

\item \textbf{Program Counter XOR Depth}: PC is for the instruction which triggered the prefetch chain.
Depth refers to the iteration count of the lookahead stages.
In general, PC is not considered as a good basis for doing lookahead prefetching as all the prefetches with depth >= 1 gets aliased onto the same PC which won't be true in actual demand fetch case.
This feature resolves a PC into a different value for each lookahead depth of SPP speculation, giving a more accurate correlation in lookahead cases.
This is akin to the concept of Virtual Program Counters\cite{VPC} introduced by Kim \textit{et. al.} for indirect branch prediction.

@@

\section{METHODOLOGY}
\subsection{Performance Model}
For testing and comparing SPP-Perc, we used ChampSim\cite{Champsim} simulator. 
ChampSim is an enhanced version of the framework that was used for the 2nd Data Prefetch Championship (DPC-2).\cite{DPC_2} 
We model model a 1-core / 4-core / 8-core Out of Order machine. The details of the configuration parameters is summarized in Table  \ref{tab:Sim_params}.

@@

The block size was fixed 64KB. Prefetching was only triggered at L2 Cache demand accesses but could be sent to L2 Cache or Last Level Cache. 
No L1 Data level prefetching was done. 
LRU replacement policy was used on all levels of cache hierarchies. 
Branch prediction was done using the perceptron branch predictor\cite{Perc_Branch}. 
Page size was kept as 4KB. 
Champsim operates all the prefetchers strictly in the physical address space.

@@

\subsection{Workloads}
This is the first time that SPEC 2017 benchmark suite\cite{SPEC2017} has been used to characterize and measure the prefetch performance. 
We use all the 20 workloads available in the SPEC 2017 Suite. 
Using SimPoint\cite{SimPoint} methodology, we identified 95 different program segments of 1 Billion instructions each.

We performed cross-validation of our SPP-Perc model using SPEC 2006\cite{SPEC2006} and CloudSuite\cite{CloudSuite} benchmarks.
For SPEC 2006, we developed 94 simpoints spread across the 29 applications.
For CloudSuite, we used the traces made available for the 2nd Cache Replacement Competition (CRC-2)\cite{CRC_2}.
The traces include 4 multi-core applications with 6 distinct phases per application. 
In total, we used 285 traces representing workloads across 53 applications.

@@

\subsection{Preferchers Simulated}
We compared SPP-Perc against three of the latest state of the art prefetchers: Best Offset Prefetcher (BOP), DRAM Aware - Access Map Pattern Matching (DA-AMPM)\cite{DA_AMPM} and Signature Path Prefecher (SPP). 
BOP was the winner of 2nd Data Prefetching Championship. 
DA-AMPM is the enhanced version of AMPM, modified to account for DRAM row buffer locality. 
SPP has been shown to outperform BOP on SPEC 2006 traces. 
For each of these, we compare their speedups taking no prefetching as the baseline.

@@

%%%%%%%%% -- BIB STYLE AND FILE -- %%%%%%%%
\bibliographystyle{ieeetr}
\bibliography{ref}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
